An Algorithmic Introduction to Lagrangian Coherent Structures

### 2013-11-11 main.tex
Correct ocean dataset graphics
Update double gyre figures to substitude backward time analysis by stretchlines.

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{variable_step_integration}
\end{center}
\caption{Schematic illustration of shearline variable time step integration. At the initial point, there is an orientation discontinuity at the lower right grid point that must be corrected prior to linear interpolation. At point \#1, no orientation discontinuties are present. At point \#2 the interpolated eigenvector field must be rotated by 180\degree\,to match the orientation at the previous point, \#1.}
\label{f:variable step integration}
\end{figure}

@@

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_forward}
\end{center}
\caption{Double gyre forward time shear (green) and hyperbolic (red) LCS.}
\label{f:double gyre hyperbolic shear lcs forward}
\end{figure}

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_backward}
\end{center}
\caption{Double gyre backward time shear (green) and hyperbolic (blue) LCS.}
\label{f:double gyre hyperbolic shear lcs backward}
\end{figure}

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_forward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs forward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines with thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:double gyre hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_backward}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs backward}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed shearlines and thick green curves are outermost shearlines, i.e. shear LCS. White dots indicate $\lambda_2$ local maximums used for strainline integration intial positions.}
\label{f:double gyre hyperbolic shear lcs details backward}
\end{figure}

Stretchlines are calculated using the function \texttt{compute\_stretchline}. Forward time stretchlines are shown in Figure~\ref{f:double gyre stretchlines forward} and backward time stretchlines are shown in Figure~\ref{f:double gyre stretchlines backward}.

\begin{figure}
\begin{center}
% demo/double_gyre/stretchlines.m, commit dbefa5a
\includegraphics[width=\textwidth]{graphics/double_gyre/stretchlines_forward}
\end{center}
\caption{Double gyre forward time stretchlines.}
\label{f:double gyre stretchlines forward}
\end{figure}

\begin{figure}
\begin{center}
% demo/double_gyre/stretchlines.m, commit dbefa5a
\includegraphics[width=\textwidth]{graphics/double_gyre/stretchlines_backward}
\end{center}
\caption{Double gyre backward time stretchlines.}
\label{f:double gyre stretchlines backward}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/variable_step_integration}
\end{center}
\caption{Schematic illustration of shearline variable time step integration. At the initial point, there is an orientation discontinuity at the lower right grid point that must be corrected prior to linear interpolation. At point \#1, no orientation discontinuties are present. At point \#2 the interpolated eigenvector field must be rotated by 180\degree\,to match the orientation at the previous point, \#1.}
\label{f:variable step integration}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_strainline}
\end{center}
\caption{Double gyre lambda-line (green) and strainline (red) LCSs.}
\label{f:double gyre hyperbolic shear lcs strainline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_stretchline}
\end{center}
\caption{Double gyre lambda-line (green) and stretchline (blue) LCSs.}
\label{f:double gyre hyperbolic shear lcs stretchline}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_strainline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs strainline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines with thick green curves being outermost closed lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_2$ local maximums used for strainline integration initial positions.}
\label{f:double gyre hyperbolic shear lcs details forward}
\end{figure}

\begin{figure}
\begin{center}
% LCS Tool commit ac3a7705aec81577b1aba3cafe598066dd689203
\includegraphics[width=\textwidth]{graphics/double_gyre/hyperbolic_shear_lcs_details_stretchline}
\end{center}
\caption{Same LCS as in Figure~\ref{f:double gyre hyperbolic shear lcs stretchline}, but with additional details. Background gray-scale is the finite-time Lyapunov exponent. Dashed green lines are Poincare sections. Green curves are closed lambda-lines and thick green curves are outermost lambda-lines, i.e. lambda-line LCSs. White dots indicate $\lambda_1$ local minimums used for stretchline integration intial positions.}
\label{f:double gyre hyperbolic shear lcs details stretchline}
\end{figure}
